---
title: "fish-coRal sandbox"
author: "Ross Cunning"
date: "3/18/2018"
output: html_document
---

```{r setup, include=FALSE}
# Set kintr options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Load libraries
library(tidyverse)  # install.packages("tidyverse")
library(cowplot)  # install.packages("cowplot")

# Load R functions
sapply(list.files(path="R/", pattern="*", full.names = TRUE), FUN=source)
```

## New parameter estimation

### kv: colony volume per unit biomass (L/C-mol^-1^)
```{r m3_Cmol, fig.width=7, fig.height=3}
# Data from:
# Jokiel PL, Morrissey JI (1986) Influence of size on primary production in the 
#   reef coral Pocillopora damicornis and the macroalga Acanthophora spicifera. 
#   Mar Biol 91:15–26

# Enter data from Table 1
df <- data_frame(
  radius.cm = c(2.1, 3.4, 4.0, 5.0, 8.2, 12.5),
  tissue.dry.wt.g = c(0.21, 1.68, 1.78, 4.60, 16.21, 34.66)
)

# Calculate colony volume (as a hemisphere) and convert biomass to Cmol
#   Assumes 41.4% carbon by weight (Schutter et al. 2010)
df <- df %>%
  mutate(vol.m3 = 2/3 * pi * (radius.cm / 100)^3,
         vol.L = vol.m3 * 1000,
         Cmol = tissue.dry.wt.g * 0.414 / 12.011)  # gBiomass * 0.414 gC/gBiomass * 1molC/12.011gC

# Plot volume as a function of biomass - fit linear and exponential
lin <- ggplot(df, aes(x=Cmol, y=vol.L)) + 
  geom_point() + 
  geom_smooth(method = "lm", se=FALSE, formula=y~x-1) +
  labs(x="Coral biomass (C-mol)", y="Coral volume (L)") +
  theme_bw()

expo <- ggplot(df, aes(x=Cmol, y=vol.L)) + 
  geom_point() + 
  geom_smooth(method = "lm", se=FALSE, formula=y~exp(x)) +
  labs(x="Coral biomass (C-mol)", y="Coral volume (L)") +
  theme_bw()

plot_grid(lin, expo)

# Calculate slope of linear fit
linmod <- lm(vol.L ~ Cmol - 1, data=df)
coef(linmod)

# Get coefficients of exponential model
expomod <- nls(vol.L ~ a * Cmol ^ b, start=c(a=1, b=1), trace=F, data=df)
#plot(vol.L ~ Cmol, data=df)
#with(df, lines(Cmol, coef(expomod)[1] * Cmol ^ coef(expomod)[2]))
coef(expomod)

```

From these data, we estimate the value for the parameter defining coral colony volume per unit biomass to be `r round(coef(linmod), 2)` L/Cmol if we use the linear fit. We could also use the (potentially better) exponential fit with coefficients a = `r round(coef(expomod)[1], 3)` and b = `r round(coef(expomod)[2], 3)`.

## Run model and explore output

### Set parameters and environment
```{r}
# Load all default parameter values for model with one Symbiodinium type
# Default parameters start with 0.001 of both hawkfish and damselfish
pars <- def_pars(nsym = 1)

# Set time vector to three years
time <- seq(0, 1825, 0.1)

# Initialize constant environment with intermediate light (15 mol/m2/d) and DIN (1e-6 M), no feeding, and no uber-predators.
env <- init_env(time=time, L=c(15,15,0), N=c(1e-6,1e-6,0), X=c(0,0,0), U=c(0,0,0))
```

### Run simulation with both fish
```{r run_model}
run1 <- run_fish_coral(time=time, env=env, par=pars)
```

### Plot coral size, interstitial [N], and associated fish biomass
```{r plot_output, fig.height=3, fig.width=10}
# Plot coral colony volume and internal nitrogen concentration
growth <- ggplot(run1, aes(x=time, y=VH)) + geom_line() +
  labs(x="Time (d)", y="Coral volume (L)",
       title="Coral growth") +
  theme_bw()

# Plot internal nitrogen concentration
interN <- ggplot(run1, aes(x=time, y=log10(Ni))) + geom_line() +
  labs(x="Time (d)", y="Interstitial N (mol/L)",
       title="log10 Nitrogen within coral head") +
  theme_bw()

# Plot fish abundance
fish <- ggplot(run1, aes(x=time)) + 
  geom_line(aes(y=W, col="Hawkfish")) +
  geom_line(aes(y=P, col="Damselfish")) +
  labs(x="Time (d)", y="Fish biomass",
       title="Coral-associated fish") +
  theme_bw() + theme(legend.position = c(0.7, 0.5))

plot_grid(growth, interN, fish, ncol = 3)
```

> Damselfish go to their carrying capacity while hawkfish go to zero. Why do hawkfish go to zero?

======

### Run simulations with hawkfish only and damselfish only

```{r}
hawk.only <- run_fish_coral(time=time, env=env, 
                            pars=replace(def_pars(), "initP", 0))
damsel.only <- run_fish_coral(time=time, env=env, 
                              pars=replace(def_pars(), "initW", 0))
```

### Plot output with hawkfish only and damselfish only

```{r, fig.width=10, fig.height=3}
# Build plots for fish biomass, interstitial N, and coral growth
fish <- ggplot() +
  geom_line(data=hawk.only, aes(x=time, y=W, color="Hawkfish only")) +
  geom_line(data=damsel.only, aes(x=time, y=P, color="Damselfish only")) +
  labs(x="Time (d)", y="Fish biomass", title="Coral-associated fish") +
  theme_bw() + theme(legend.position = c(0.7, 0.5))

interN <- ggplot() +
  geom_line(data=hawk.only, aes(x=time, y=log10(Ni), color="Hawkfish only")) +
  geom_line(data=damsel.only, aes(x=time, y=log10(Ni), color="Damselfish only")) +
  labs(x="Time (d)", y="log10 Interstitial N (mol/L)", title="Nitrogen within coral head") +
  theme_bw() + theme(legend.position = c(0.7, 0.5))

growth <- ggplot() +
  geom_line(data=hawk.only, aes(x=time, y=VH, color="Hawkfish only")) +
  geom_line(data=damsel.only, aes(x=time, y=VH, color="Damselfish only")) +
  labs(x="Time (d)", y="Coral volume (L)", title="Coral growth") +
  theme_bw() + theme(legend.position = c(0.7, 0.2))

# Plot multipanel figure comparing hawkfish only to damselfish only dynamics
plot_grid(fish, interN, growth, ncol=3)
```

> Coral with damselfish supports more total fish biomass, has higher interstitial nitrogen concentrations, and grows faster, than the coral with hawkfish.
