---
title: "fish-coRal sandbox"
author: "Ross Cunning"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
# Set kintr options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE)

# Load libraries
library(tidyverse)  # install.packages("tidyverse")
library(cowplot)  # install.packages("cowplot")

# Load R functions
sapply(list.files(path="R/", pattern="*", full.names = TRUE), FUN=source)
```

# Both fish
```{r run_model}
# Set time vector to three years
time <- seq(0, 1095, 0.1)
# Initialize constant environment
env <- init_env(time=time, L=c(15,15,0), N=c(1e-7,1e-7,0), X=c(0,0,0), U=c(0,0,0))
# Run simulation
run1 <- run_fish_coral(time=time, env=env, par=def_pars(initW=1, initP=1))
```

#### Plot coral size, interstitial [N], and associated fish biomass
```{r plot_output, fig.height=3, fig.width=10}
# Plot coral colony volume and internal nitrogen concentration
growth <- ggplot(run1, aes(x=time, y=VH)) + geom_line() +
  labs(x="Time (d)", y="Coral volume (L)", title="Coral growth") +
  theme_bw()

# Plot internal nitrogen concentration
interN <- ggplot(run1, aes(x=time, y=log10(Ni))) + geom_line() +
  labs(x="Time (d)", y="log10 Interstitial N (mol/L)",
       title="Nitrogen within coral head") +
  theme_bw()

# Plot fish abundance
fish <- ggplot(run1, aes(x=time)) + ylim(0, 1) +
  geom_line(aes(y=W/VH, col="Hawkfish")) +
  geom_line(aes(y=P/VH, col="Damselfish")) +
  geom_line(aes(y=S/H, col="Symbiodinium")) +
  labs(x="Time (d)", y="Fish biomass (per coral-Liter)",
       title="Coral-associated fish") +
  theme_bw() + theme(legend.position = c(0.7, 0.5))

plot_grid(growth, interN, fish, ncol = 3)
```

> Damselfish go to their carrying capacity while hawkfish go to zero. Why do hawkfish go to zero?


# Hawkfish or damselfish alone

```{r run_hawkonly_damonly}
  hawk.only <- run_fish_coral(time=time, env=env, pars=def_pars(initW=1, initP=0))
damsel.only <- run_fish_coral(time=time, env=env, pars=def_pars(initW=0, initP=1))
```

#### Plot output with hawkfish only and damselfish only

```{r, fig.width=10, fig.height=3}
# Build plots for fish biomass, interstitial N, and coral growth
fish <- ggplot() +
  geom_line(data=hawk.only, aes(x=time, y=W/VH, color="Hawkfish only")) +
  geom_line(data=damsel.only, aes(x=time, y=P/VH, color="Damselfish only")) +
  labs(x="Time (d)", y="Fish biomass (per coral-Liter)", title="Coral-associated fish") +
  theme_bw() + theme(legend.position = c(0.7, 0.5))

interN <- ggplot() +
  geom_line(data=hawk.only, aes(x=time, y=log10(Ni), color="Hawkfish only")) +
  geom_line(data=damsel.only, aes(x=time, y=log10(Ni), color="Damselfish only")) +
  labs(x="Time (d)", y="log10 Interstitial N (mol/L)", title="Nitrogen within coral head") +
  theme_bw() + theme(legend.position = c(0.7, 0.2))

growth <- ggplot() +
  geom_line(data=hawk.only, aes(x=time, y=VH, color="Hawkfish only")) +
  geom_line(data=damsel.only, aes(x=time, y=VH, color="Damselfish only")) +
  labs(x="Time (d)", y="Coral volume (L)", title="Coral growth") +
  theme_bw() + theme(legend.position = c(0.7, 0.5))

# Plot multipanel figure comparing hawkfish only to damselfish only dynamics
plot_grid(growth, interN, fish, ncol=3)
```

> Coral with damselfish supports more total fish biomass, has higher interstitial nitrogen concentrations, and grows faster, than the coral with hawkfish.

# No fish

```{r run_nofish}
nofish <- run_fish_coral(time=time, env=env, pars=def_pars(initW=0, initP=0))
```

#### Plot output with no fish

```{r, fig.width=10, fig.height=3}
# Build plots for fish biomass, interstitial N, and coral growth
fish <- ggplot() +
  geom_line(data=nofish, aes(x=time, y=W/VH)) +
  labs(x="Time (d)", y="Fish biomass (per coral-Liter)", title="Coral-associated fish") +
  theme_bw() + theme(legend.position = c(0.7, 0.5))

interN <- ggplot() +
  geom_line(data=hawk.only, aes(x=time, y=log10(Ni))) +
  labs(x="Time (d)", y="log10 Interstitial N (mol/L)", title="Nitrogen within coral head") +
  theme_bw() + theme(legend.position = c(0.7, 0.2))

growth <- ggplot() +
  geom_line(data=hawk.only, aes(x=time, y=VH)) +
  labs(x="Time (d)", y="Coral volume (L)", title="Coral growth") +
  theme_bw() + theme(legend.position = c(0.7, 0.5))

# Plot multipanel figure comparing hawkfish only to damselfish only dynamics
plot_grid(growth, interN, fish, ncol=3)
```
